SpARC: Sparse Redundant Calibration

### 2016-09-26 paper.tex
red mapping section

Eq.~\eqref{eq:vis_definition} can also be expressed in the following vector form 
\begin{equation}
\bd = \bv + \bn, 
\end{equation}
where 
\begin{eqnarray}
 \bd &=& [d_{pq}] \big \} ~ [pq] = 1\cdots N ~ (p<q),\nonumber\\
 \bv &=& [g_p y_{pq}\conj{g}_q]  \big \} ~ [pq] = 1\cdots N ~ (p<q),\nonumber\\
 \bn &=& [n_{pq}]  \big \} ~ [pq] = 1\cdots N ~ (p<q).\label{eq:vec_definitions}
\end{eqnarray}
In Eq.~\eqref{eq:vec_definitions}, $N$ denotes the number of antennas in the array.

@@

\subsection{Redundant Array Geometry Mapping}
If an array is redundant then its redundant baselines sample the exact same visibilites in the $uv$-plane, i.e. if baseline $pq$ and $rs$ are redundant then $y_{pq} = y_{rs}$. We can
therefore also use the following useful indexing strategy: we can use singular redundant baseline indexes instead of composite antenna pairs to label the true observed visibilities.

>>>>

\subsection{Redundant Array Geometry Mapping}
If an array is redundant then its redundant baselines sample the exact same visibilites in the $uv$-plane, i.e. if baseline $pq$ and $rs$ are redundant then $y_{pq} = y_{rs}$. We can
therefore also use the following useful indexing strategy: We can use singular redundant baseline indexes instead of composite antenna pairs to label the true observed visibilities.

Let $\phi_{ij}:\mathbb{N}^2\rightarrow\mathbb{N}^+$ be the mapping that maps composite antenna pairs to the unique redundant baseline indexes of an array. This mapping is not symmetric as 
$\phi_{ij} = 0$ if $i>j$. It is possible to construct a simple analytic expression for $\phi_{ij}$ when our array is in an east-west regular configuration:
\begin{equation}
\phi_{ij} = 
\begin{cases}
j-i&\textrm{if}~i<j\\
0&\textrm{otherwise}
\end{cases}.
\end{equation}
It becomes increasingly more difficult to construct analytic expressions of $\phi_{ij}$ for other more complicated array layouts.

We can also define the following symmetric variant of $\phi_{ij}$:
\begin{equation}
\zeta_{ij} = 
\begin{cases}
\phi_{ij}~\textrm{if}~i\leq j\\
\phi_{ji}~\textrm{if}~i>j
\end{cases}.
\end{equation} 
If the mapping $\phi_{ij}$ is known and one is given one of the two antenna indexes that together form a redundant baseline as well as the redundant baseline index itself then it is possible 
to calculate the unknown antenna index. This can be calculated via the following two expressions:
\begin{equation}
\xi_{ij} = 
\begin{cases}
p~\textrm{if}~\exists! ~ p \in \mathbb{N} ~ s.t. ~(\phi_{pi} = j)\\
0~\textrm{otherwise}
\end{cases},
\end{equation}
and
\begin{equation}
\psi_{ij} = 
\begin{cases}
q~\textrm{if}~\exists! ~ q \in \mathbb{N} ~ s.t. ~(\phi_{iq} = j)\\
0~\textrm{otherwise}
\end{cases}
\end{equation}

We use $\xi_{ij}$ to retrieve the first antenna index of the composite antenna pair associated with a particular baseline if the index of the first antenna in the composite antenna pair and the unique redundant baseline index are known, while we use $\psi_{ij}$ to obtain 
a similar result; the second antenna index of the composite antenna pair. \textbf{NB::} I still need to plot $\zeta_{ij}$ for different antenna layouts.

If the array is redundant and the mapping $\phi_{ij}$ is known we can rewrite Eq.~\eqref{eq:vis_definition} as
\begin{equation}
\label{eq:vis_red}
d_{pq} = g_{p}\conj{g}_{q}y_{\phi_{pq}} + n_{pq}.
\end{equation}
Eq.~\eqref{eq:vis_red} can also be expressed in the following vector form 
\begin{equation}
\bd = \bv + \bn, 
\end{equation}
where 
\begin{eqnarray}
 \bd &=& [d_{pq}] \big \} ~ [pq] = 1\cdots N ~ (p<q),\nonumber\\
 \bv &=& [g_p y_{\phi_{pq}} \conj{g}_q]  \big \} ~ [pq] = 1\cdots N ~ (p<q),\nonumber\\
 \bn &=& [n_{pq}]  \big \} ~ [pq] = 1\cdots N ~ (p<q).\label{eq:vec_definitions}
\end{eqnarray}
In Eq.~\eqref{eq:vec_definitions}, $N$ denotes the number of antennas in the array. NB --- above equation is wrong, needs to be baselines ...

@@
